Critical Temperature of the Ising Ferromagnet on Proximity Graphs derived from Square Lattices by Site Displacement

### 2015-12-02 Tex/paper/abstract.tex
Paper Entwurf 3. Iteration (Meine Korrekturen)

We perform Monte Carlo simulations to determine the critical temperatures
of Ising Ferromagnets (IFM) on proximity graphs with different underlying
node-sets, which can be governed by a parameter $\sigma$.
The coupling strengths arise from the Euclidean distance
between coupled spins.
The simulations are carried out on graphs with \(N=16^{2}\) to \(N=128^{2}\)
nodes utilizing the Wolff cluster algorithm and parallel tempering in a
wide temperature range around the critical point to measure the Binder Cumulant.
The critical temperatures are shown to depend mainly on the average degree
and the type of the underlying proximity graph.
We further verify using finite-size scaling methods that the IFM on proximity
graphs is in the same universality class as the IFM on a two-dimensional
square lattice.

>>>>

We perform Monte Carlo simulations to determine the critical temperatures
of Ising Ferromagnets (IFM) on proximity graphs with different underlying
node sets, which can be governed by a parameter $\sigma$.
The coupling strengths arise from the Euclidean distance
between coupled spins.
The simulations are carried out on graphs with \(N=16^{2}\) to \(N=128^{2}\)
nodes utilizing the Wolff cluster algorithm and parallel tempering in a
wide temperature range around the critical point to measure
the Binder cumulant as means to obtain the critical temperature.
The critical temperatures are shown to depend mainly on the average degree
and the type of the underlying proximity graph.
We further verify using finite-size scaling methods that the IFM on proximity
graphs is in the same universality class as the IFM on a two-dimensional
square lattice.

### 2015-12-02 Tex/paper/conclusion.tex
Paper Entwurf 3. Iteration (Meine Korrekturen)

\label{sec:conclusion}
This study shows that universality of the Ising model is preserved for
irregular graphs on a wide range of configurations which are intermediate
between the square lattice ising model and a random Poisson point process.
Also the critical temperature was measured over this range and determined
that it shows in first approximation a power law behavior with the mean
number of neighbors as the base and an exponent dependent on the
graph type that defines the neighbor relationships.

@@

The next step would be the extension of this model to three and higher
dimensions, where the used proximity graphs are still well defined. It
would also be worthwhile to study properties of the graph ensembles itself,
because -- to our knowledge -- they are mostly studied in 2D \cite{RNGCell}.

>>>>

\label{sec:conclusion}
This study shows that universality of the Ising model is preserved for
irregular graphs on a wide range of configurations which are intermediate
between the square lattice Ising model and a random Poisson point process.
Also the critical temperature was measured over this range and determined
that it shows approximately a power law behavior with the mean
number of neighbors as the base and an exponent dependent on the
graph type that defines the neighbor relationships.

@@

The next step would be the extension to three and higher
dimensions, where the used proximity graphs are still well defined. It
would also be worthwhile to study properties of the graph ensembles themselves,
because -- to our knowledge -- they are mostly studied in 2D \cite{RNGCell}.

### 2015-12-02 Tex/paper/introduction.tex
Paper Entwurf 3. Iteration (Meine Korrekturen)

The Ising model for a ferromagnet \cite{Ising1925} is perhaps the
most extensive studied model in statistical mechanics. It consists
of spins which can point up or down and interact with neighboring
spins. It shows a second order phase transition separating a
ferromagnetic and a paramagnetic phase. While there exist analytic
solutions\cite{Onsager1944,Wannier1945} describing the phase
transition for Ising models on regular lattices in two dimensions,
higher dimensional lattices and non-regular lattices are primarily studied
by Monte Carlo simulations.

Some work \cite{Janke1994,Lima2000,Lima2008} was done to determine
the critcal temperatures and confirm the universality of two-dimensional IFM
where the spins are arranged randomly in the unit square by a
Poisson point process and neighbor relationships are determined by a
Delaunay triangulation that maintains the planarity of the system.
This article extends the former research to other
irregular lattices, namely the Relative Neighborhood graph (RNG) and
Gabriel graph (GG), which belong, as the Delaunay triangulation, to the
family of \emph{proximity graphs}. To get some intuition for proximity
graphs, their purpose is to connect nodes which are close to each other.
Hence they are suited to generalize problems defined on regular lattices
with nearest neighbor relationships.
This family of graphs have been applied in geographic variation studies in
biology \cite{Sokal1978,Sokal1980,Selander1975} and as potential candidate for ``virtual backbones'' in ad-hoc
networks \cite{Kuhn2003,Bose2001,Santi2005,Karp2000,jennings2002topology}. % also machine learning

Beginning with a square lattice the nodes can be shifted randomly governed
by a tunable parameter $\sigma$ until the distribution of the nodes is
indistinguishable from a Poisson point process.
For every realization of nodes, the construction rules for the proximity
graph at hand define an edge-set.
%~ The edge-set for any realization of node-placements is well defined by
%~ the construction rules of the
We measure the critical temperatures by varying $\sigma$ and confirm that
the universality class does not change in the process.

>>>>

The Ising model for a ferromagnet \cite{Ising1925} is perhaps the
most extensive studied model in statistical mechanics. It consists
of spins which can point up or down and interact with neighboring
spins. It shows a second order phase transition separating a
ferromagnetic from a paramagnetic phase. While there exist analytic
solutions\cite{Onsager1944,Wannier1945} describing the phase
transition for Ising models on regular lattices in two dimensions,
higher dimensional lattices and non-regular lattices are primarily studied
by Monte Carlo simulations.

Some work \cite{Janke1994,Lima2000,Lima2008} was done to determine
the critcal temperatures and confirm the universality of two-dimensional IFM
where the spins are arranged randomly in the unit square by a
Poisson point process and neighbor relationships are determined by a
Delaunay triangulation that maintains the planarity of the system.
This article extends the former research to other
irregular lattices, namely the Relative Neighborhood graph (RNG) and
Gabriel graph (GG), which belong together with the Delaunay triangulation,
to the family of \emph{proximity graphs}. The purpose of proximity graphs
is to connect nodes which are close to each other, hence they are suited
to generalize problems defined on regular lattices with nearest neighbor
relationships.
This family of graphs have been applied in geographic variation studies in
biology \cite{Sokal1978,Sokal1980,Selander1975} and as potential candidates for ``virtual backbones'' in ad-hoc
networks \cite{Kuhn2003,Bose2001,Santi2005,Karp2000,jennings2002topology}. % also machine learning

Beginning with a square lattice the nodes can be shifted randomly governed
by a tunable parameter $\sigma$ until the distribution of the nodes is
indistinguishable from a Poisson point process.
For every realization of nodes, the construction rules for the proximity
graph at hand define an edge set.
%~ The edge-set for any realization of node-placements is well defined by
%~ the construction rules of the
We measure the critical temperatures for a range of $\sigma$ and confirm that
the universality class does not change in the process.

### 2015-12-02 Tex/paper/model.tex
Paper Entwurf 3. Iteration (Meine Korrekturen)

\label{sec:model}
\subsection{Proximity Graphs}
\label{ssec:graphtypes}
    A graph \(G(V,E)\) consists of a set of nodes \(V\) and edges \(E \subset V^{2}\).
    Two nodes connected by an edge are neighbors.
    Proximity graphs are defined in a metric space. In this article a
    two-dimensional space with the Euclidean metric is chosen, because
    it is the most common case and easy to visualize, though in principle
    every metric in any dimension can be used.

    The \emph{Relative Neighborhood graph} (RNG) \cite{Toussaint1980} is
    a proximity graph. Two nodes \(i\) and \(j\) with distance $d_{ij}$
    will be connected, if no other node is in the \emph {lune}. The lune
    is defined as the intersection of two circles with radius \(r =
    d_{ij}\) and centers on \(i\) and \(j\). That means that the edge
    $\{ij\}$ is part of the graph, if the condition
    \[d_{ij} \le \max\left\{ d_{ik} + d_{kj} \right\} \forall k \in V\setminus\{i,j\}\]
    is fulfilled. See also the hatched region
    in Fig.~\ref{fig:lunes}. An example is given in Fig.~\ref{sfig:lunes:rng}.

    \begin{figure}[htbp]
        \centering
        \subfigure[]{
            \label{sfig:lunes:def}
            \includegraphics[width=0.14\textwidth]{images/GG_RNG_def}
        }
        \subfigure[]{
            \label{sfig:lunes:rng}
            \includegraphics[width=0.14\textwidth]{images/RNG/L12S03}
        }
        \subfigure[]{
            \label{sfig:lunes:gg}
            \includegraphics[width=0.14\textwidth]{images/GG/L12S03}
        }
        \caption[Gabriel and Relative Neighborhood Graph]
        {
            \subref{sfig:lunes:def} Lunes, which define whether an edge
                exist, of RNG (hatched region) and GG (cross hatched region).
                It is evident from this sketch that the GG is a supergraph
                of the RNG. If there is an edge in the RNG, the hatched
                region contains no node, then of course also the double
                hatched region contains no node and thus this edge appears
                also in the GG. So every egde of the RNG is also present
                in a GG on the same set of nodes.
            \subref{sfig:lunes:rng} Example of a RNG on periodic
                boundary conditions.
            \subref{sfig:lunes:gg} Example of a GG on
                periodic boundary conditions. Periodic nodes are dashed.
        }
        \label{fig:lunes}
    \end{figure}

    The \emph{Gabriel graph} (GG) \cite{Gabriel1969} is a subgraph
    of the Delaunay triangulation \cite{Delaunay1934,Katajainen}
    (DT), i.e.~for the same set of nodes \(V\) the edge set of the
    DT is a superset of the edge set of the GG. Two nodes \(i\) and
    \(j\) with distance \(d_{ij}\) will be connected with an edge,
    if a circle with its center on half way between \(i\) and \(j\)
    and radius \(r = \frac{d_{ij}}{2}\) contains no other nodes, i.e.~the
    condition
    \[d_{ij} < d_{ik} + d_{kj} \forall k \in V\setminus\{i,j\}\]
    is fulfilled. See
    also the cross hatched region from Fig.~\ref{sfig:lunes:def}. An
    example is given in Fig.~\ref {sfig:lunes:gg}. Note that the
    lune of the GG is completely enclosed in the lune of the RNG,
    therefore the RNG is a subgraph of the GG.

@@

\subsection{The Ising Model}
\label{ssec:model}
    Commonly, the IFM is studies on a square lattice with lateral length
    \(L\) and \(N=L^2\) nodes with periodic boundary conditions.
    Each site $i$ has an Ising spin \(s_i \in \{-1,+1\}\) and interacts with its
    nearest neighbors described by the Hamiltonian
    \begin{equation}
        \mathcal{H} = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}.
        \label{eq:hamiltonian}
    \end{equation}
    \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are
    nearest neighbors, i.e.~they are connected by an edge.
    The coupling strength between \(i\) and \(j\) is given by
    \(J_{ij}\).

    In this article the nodes of the square lattice are
    displaced, introducing geometric disorder resulting in a non regular graph
    structure.
    The displacement is randomly Gaussian distributed with standard
    deviation \(\sigma\), i.e.~the \(x\) and \(y\) coordinates of the
    sites are displaced by random \(\Delta x\) and \(\Delta y\) drawn
    from a Gaussian distribution with zero mean.
    In the following \(\sigma\) will be called \emph{disorder parameter}.
    If we took ``nearest neighbor" in the Euclidean meaning, most sites
    would only have one nearest neighbor after the
    displacement. If only the edges between these neighbors remained,
    the lattice would collapse to many very small clusters. If on the
    other hand all edges remained as they were before the displacement,
    edges might cross each other -- at least for big displacements.
    The crossing of edges would destroy the planar character of the graph.
    To avoid this, a new edge-set will be established after the displacement
    to form a proximity graph. The influence of $\sigma$ on the
    structure of a proximity graph is shown in Fig.~\ref{fig:RNG_sigma}
    for a RNG.
    \begin{figure}[htb]
        \centering
        \subfigure[$\sigma = 0.09$]
        {
            \label{sfig:RNG_sigma:0.09}
            \includegraphics[width=0.14\textwidth]{images/RNG/out009}
        }
        \subfigure[$\sigma = 0.15$]
        {
            \label{sfig:RNG_sigma:0.15}
            \includegraphics[width=0.14\textwidth]{images/RNG/out015}
        }
        \subfigure[$\sigma = 0.21$]
        {
            \label{sfig:RNG_sigma:0.21}
            \includegraphics[width=0.14\textwidth]{images/RNG/out021}
        }
        \caption[Examples of RNG for different $\sigma$]
        {
            Examples of proximity graphs (more precise, Relative Neighborhood
            graph see Sec. \ref{ssec:graphtypes}) for different $\sigma$.
            Connections which cross a periodic boundary are indicated
            by edges which connect a solid node to a dashed node.
        }
        \label{fig:RNG_sigma}
    \end{figure}
    The coupling constants \(J_{ij}\), i.e.~edge weights, depend on the
    geometric distance between the connected pair of sites. More precise,
    the weight of an edge is
    \begin{equation}
        E_{ij} = J_{ij} = \mathrm{e}^{\alpha (1-d_{ij})},
        \label{eq:coupling}
    \end{equation}
    where \(d_{ij}\) is the Euclidean
    distance between node \(i\) and \(j\). Following Ref.~\cite{Lima2000}
    the free parameter \(\alpha\) is set to \(\alpha = 0.5\).
    Note that for \(\sigma = 0\) the resulting \(d_{ij} = 1\) and therefore
    \(J_{ij} = 1\) for every edge $\{i,j\}$. Consequently, in this case
    the graph is a common square lattice.

>>>>

\label{sec:model}
\subsection{Proximity Graphs}
\label{ssec:graphtypes}
    A graph \(G(V,E)\) consists of a set of nodes \(V\) and edges \(E \subset V^{2}\).
    Two nodes connected by an edge are called neighbors.
    Proximity graphs are defined in a metric space. In this article a
    two-dimensional space with the Euclidean metric is chosen, because
    it is the most common case and easy to visualize, though in principle
    every metric in any dimension can be used.

    The \emph{Relative Neighborhood graph} (RNG) \cite{Toussaint1980} is
    a proximity graph. Two nodes \(i\) and \(j\) with distance $d_{ij}$
    will be connected, if no other node is in the \emph {lune}. The lune
    is defined as the intersection of two circles with radius \(r =
    d_{ij}\) and centers on \(i\) and \(j\). That means that the edge
    $\{i,j\}$ is part of the graph, if the condition
    \begin{align*}
        d_{ij} &\le \max\left\{ d_{ik} + d_{kj} \right\} &\forall k \in V\setminus\{i,j\}
    \end{align*}
    is fulfilled. See also the hatched region
    in Fig.~\ref{fig:lunes}. An example is given in Fig.~\ref{sfig:lunes:rng}.

    \begin{figure}[htbp]
        \centering
        \subfigure[]{
            \label{sfig:lunes:def}
            \includegraphics[width=0.14\textwidth]{images/GG_RNG_def}
        }
        \subfigure[]{
            \label{sfig:lunes:rng}
            \includegraphics[width=0.14\textwidth]{images/RNG/L12S03}
        }
        \subfigure[]{
            \label{sfig:lunes:gg}
            \includegraphics[width=0.14\textwidth]{images/GG/L12S03}
        }
        \caption[Gabriel and Relative Neighborhood Graph]
        {
            \subref{sfig:lunes:def} Lunes, which define whether an edge
                exists, of RNG (hatched region) and GG (cross hatched region).
                It is evident from this sketch that the GG is a supergraph
                of the RNG. If there is an edge in the RNG, the hatched
                region contains no node, then of course also the double
                hatched region contains no node and thus this edge appears
                also in the GG. So every egde of the RNG is also present
                in a GG on the same set of nodes.
            \subref{sfig:lunes:rng} Example of a RNG on periodic
                boundary conditions.
            \subref{sfig:lunes:gg} Example of a GG on
                periodic boundary conditions. Periodic nodes are dashed.
        }
        \label{fig:lunes}
    \end{figure}

    The \emph{Gabriel graph} (GG) \cite{Gabriel1969} is a subgraph
    of the Delaunay triangulation \cite{Delaunay1934,Katajainen}
    (DT), i.e.~for the same set of nodes \(V\) the edge set of the
    DT is a superset of the edge set of the GG. Two nodes \(i\) and
    \(j\) with distance \(d_{ij}\) will be connected with an edge,
    if a circle with its center on half way between \(i\) and \(j\)
    and radius \(r = \frac{d_{ij}}{2}\) contains no other nodes, i.e.~the
    condition
    \begin{align*}
        d_{ij} &< d_{ik} + d_{kj} &\forall k \in V\setminus\{i,j\}
    \end{align*}
    is fulfilled. See
    also the cross hatched region from Fig.~\ref{sfig:lunes:def}. An
    example is given in Fig.~\ref {sfig:lunes:gg}. Note that the
    lune of the GG is completely enclosed in the lune of the RNG,
    therefore the RNG is a subgraph of the GG.

@@

\subsection{The Ising Model}
\label{ssec:model}
    Commonly, the IFM is studied on a square lattice with lateral length
    \(L\) and \(N=L^2\) nodes with periodic boundary conditions.
    Each node $i$ has an Ising spin \(s_i \in \{-1,+1\}\) and interacts with its
    nearest neighbors described by the Hamiltonian
    \begin{equation}
        \mathcal{H} = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}.
        \label{eq:hamiltonian}
    \end{equation}
    \(\avg{i,j}\) refers to nodes \(i\) and \(j\) which are
    nearest neighbors, i.e.~they are connected by an edge.
    The coupling strength between \(i\) and \(j\) is given by
    \(J_{ij}\).

    In this article the nodes of the square lattice are
    displaced, introducing geometric disorder resulting in a non-regular graph
    structure.
    The displacement is randomly Gaussian distributed with standard
    deviation \(\sigma\), i.e.~the \(x\) and \(y\) coordinates of the
    nodes are displaced by random \(\Delta x\) and \(\Delta y\) drawn
    from a Gaussian distribution with zero mean.
    In the following, \(\sigma\) will be called \emph{disorder parameter}.
    If we took ``nearest neighbor" in the Euclidean meaning, most nodes
    would only have one nearest neighbor after the
    displacement. If only the edges between these neighbors remained,
    the lattice would collapse to many very small clusters. If, on the
    other hand, all edges remained as they were before the displacement,
    edges might cross each other -- at least for big displacements.
    The crossing of edges would destroy the planar character of the graph.
    To avoid this, a new edge set will be established after the displacement
    to form a proximity graph. The influence of $\sigma$ on the
    structure of a proximity graph is shown in Fig.~\ref{fig:RNG_sigma}
    for a RNG.
    \begin{figure}[htb]
        \centering
        \subfigure[$\sigma = 0.09$]
        {
            \label{sfig:RNG_sigma:0.09}
            \includegraphics[width=0.14\textwidth]{images/RNG/out009}
        }
        \subfigure[$\sigma = 0.15$]
        {
            \label{sfig:RNG_sigma:0.15}
            \includegraphics[width=0.14\textwidth]{images/RNG/out015}
        }
        \subfigure[$\sigma = 0.21$]
        {
            \label{sfig:RNG_sigma:0.21}
            \includegraphics[width=0.14\textwidth]{images/RNG/out021}
        }
        \caption[Examples of RNG for different $\sigma$]
        {
            Examples of proximity graphs (more precise, Relative Neighborhood
            graph see Sec. \ref{ssec:graphtypes}) for different values of $\sigma$.
            Connections which cross a periodic boundary are indicated
            by edges which connect a solid node to a dashed node.
        }
        \label{fig:RNG_sigma}
    \end{figure}
    The coupling constants \(J_{ij}\), i.e.~edge weights, depend on the
    geometric distance between the connected pair of nodes. More precise,
    the weight of an edge is
    \begin{equation}
        E_{ij} = J_{ij} = \mathrm{e}^{\alpha (1-d_{ij})},
        \label{eq:coupling}
    \end{equation}
    where \(d_{ij}\) is the Euclidean
    distance between node \(i\) and \(j\). Following Ref.~\cite{Lima2000}
    the free parameter \(\alpha\) is set to \(\alpha = 0.5\).
    Note that for \(\sigma = 0\) the resulting \(d_{ij} = 1\) and therefore
    \(J_{ij} = 1\) for every edge $\{i,j\}$. Consequently, in this case
    the graph is a common square lattice.

### 2015-12-02 Tex/paper/results.tex
Paper Entwurf 3. Iteration (Meine Korrekturen)

\label{sec:results}
The results are obtained through Monte Carlo simulations. For each
sweep \(N\) single spin flip Metropolis updates \cite{Metropolis1953},
one Wolff cluster update \cite{Wolff1989} and one
parallel tempering swap \cite{ParallelTempering1986} are performed.
For every system size $L \in \{16,32,64,128\}$ and 19 different
$\sigma \in [0,1.2]$ on $100$ different realizations at least $5000$
independent measurements are taken in equilibrium.\\
Since it is not known beforehand, where the critical temperatures \(T_c\)
are located, the Wolff cluster algorithm is used at every
temperature. Albeit the efficiency of the algorithmic procedure was
not examined for every temperature, the speed up near criticality
should be worth the moderate slow down at other temperatures.\\

@@

magnetization, the susceptiblity and the Binder parameter

@@

        The same procedure is used on the Binder parameter $g$ and the
        magnetization $|m|$ to to determine the critical exponents

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[scale=1]{plots/Binder_over_Correlation_All}
    \caption[Binder Cumulant over two-point finite-size correlation function divided by system size]
    {
        Binder Cumulant over two-point finite-size correlation function
        divided by system size. The datapoints for different system sizes
        are drawn with different symbols, while the datapoints for different
        graph ensembles are drawn with different colors. Anyway, all points
        fall on one curve within errorbars.
        %~ The inset zooms into the plot to show that
        %~ all datapoints fall within errorbars onto one curve.
    }
    \label{fig:binderOverCorr}
\end{figure}
If the Binder parameter
\[g = \frac{3}{2}\brac{1-\frac{\avgR{\avg{m^4}}}{3\avgR{\avg{m^2}^2}}}\]
is plotted over $\xi$ for different $\sigma$, $L$ and $T$ as shown in
Fig.~\ref{fig:binderOverCorr} all data points fall on the
same curve, which confirms that this IFM on proximity graphs is in the
same universality class as on the square lattice, i.e.~$\sigma=0$.

This study examines the critical temperatures $T_c$ for different $\sigma$.
Therefore the knowledge that the Binder parameters $g$ for different
system sizes $L$ intersect at $T_c$ \cite{Binder1981} as shown in Fig.~\ref{sfig:Tc:binder}
%~ \begin{figure*}[hbtp]
    %~ \centering
    %~ \subfigure{
        %~ \label{sfig:Tc:binder}
        %~ \includegraphics[scale=1]{plots/binder}
    %~ }
    %~ \subfigure{
        %~ \label{sfig:Tc:RNG}
        %~ \includegraphics[scale=1]{plots/Tc_RNG}
    %~ }
    %~ \subfigure{
        %~ \label{sfig:Tc:GG}
        %~ \includegraphics[scale=1]{plots/Tc_GG}
    %~ }
    %~ \caption[Critical Temperature over Different Disorder Parameters]
    %~ {
        %~ Critical temperatures \(T_c\) are obtained by finding the intersections
        %~ of the Binder parameters $g$ for different system sizes $L$.
        %~ They are plotted over different disorder parameters \(\sigma\).
        %~ Interesting points are the jump and rise of the GG at small
        %~ \(\sigma\) and the plateau on the RNG for small \(\sigma\).
    %~ }
    %~ \label{fig:Tc}
%~ \end{figure*}
\begin{figure*}[hbtp]
    \subfigure[]{
        \label{sfig:Tc:binder}
        \includegraphics[scale=1]{plots/binder}
    }
    \subfigure[]{
        \label{sfig:Tc:RNG}
        \label{sfig:Tc:GG}
        \includegraphics[scale=1]{plots/Tc_both}
    }
    \subfigure[]{
        \label{fig:TcK}
        \includegraphics[scale=1]{plots/TcK}
    }
    \caption[Critical Temperature over Different Disorder Parameters]
    {
        \subref{sfig:Tc:binder} Critical temperatures \(T_c\) are obtained by finding the intersections
        of the Binder parameters $g$ for different system sizes $L$.
        \subref{sfig:Tc:RNG} They are plotted over different disorder parameters \(\sigma\).
        Interesting points are the jump and rise of the GG at small
        \(\sigma\) and the plateau on the RNG for small \(\sigma\).
        \subref{fig:TcK} \(T_c\) is plotted in a log-log plot as a function of the degree $K$.
        The lines are fits to a power law function \(T_c = aK^b\)
        ignoring the ``bulk" of points in the lower left and upper right, where
        deviations from the power law become obvious.
        For the RNG the fit yields $b = 1.349(2)$ with $\chi_\mathrm{red}^2 = 1.9$
        and for the GG  $b = 1.300(5)$ with $\chi_\mathrm{red}^2 = 0.8$
    }
    \label{fig:Tc}
\end{figure*}
is used.
Since \(g\) is only measured for discrete values of \(T\),
the points have to be interpolated to find the intersection. Therefore
a \emph{cubic spline} \cite{press2007numerical} interpolation %footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
is calculated for the measured points.
%~ Cubic spline interpolation is a piece-wise fitting of polynoms of
%~ degree three which are joined under the condition to be at least two
%~ times continuously differentiable.
%~ This interpolation type has the
%~ advantage that it is only influenced by local points so that the
%~ plateaus at low and high \(T\) do not influence the interpolation in
%~ the vicinity of \(T_c\) -- in contrast to, e.g.\ an polynom fit of
%~ degree 4, which has to be restricted to the vincinity of \(T_c\) to
%~ yield meaningful results.
An even better method would be the
\emph{multiple histogram} method \cite[p. 219ff]{NewmanBarkema1999}.
But the simple cubic spline interpolation seems to deliver results that
are good enough, because the temperatures of the measurements are
sufficiently near to each other. Also a cubic spline interpolation is
far easier to obtain.

The first oddity in Fig.~\ref{sfig:Tc:GG} which needs to be addressed is
the jump of $T_c$ close to $\sigma = 0$, where it jumps from $T_c(0) = 2.269(1)$
to $T_c(0.03) = 2.851(1)$ at the next measured temperature. This is easily explainable,
because the square lattice at $\sigma = 0$ is a very special case for the
GG and at smallest deviations from the square lattice new edges arise in
the GG, which lead to a stronger coupling of spins such that the system stays
ferromagnetic at higher temperatures.

@@

The critical temperature $T_c$ decreases with increasing $\sigma$, which
is expected, since the number of edges decreases, which can be seen in
Fig.~\ref{fig:RNG_sigma} and with loosely coupled spins, the temperature
needed to disturb the ferromagnetic phase is lower than with strong coupled
spins. To quantify the influence of this, $T_c$ is plotted over the
degree $K$, i.e.~the mean number of neighbors each spin has, in Fig.~\ref{fig:TcK}.
For a given graph type, $T_c$ can be derived approximately by a power law
from $K$. But there are deviations from this behavior, which reflect
at least the influence of the coupling constant $J$.

>>>>

\label{sec:results}
The results are obtained through Monte Carlo simulations. For each
sweep \(N\) single spin flip Metropolis updates \cite{Metropolis1953},
one Wolff cluster update \cite{Wolff1989} and one
parallel tempering swap \cite{ParallelTempering1986} are performed.
For every system size $L \in \{16,32,64,128\}$ and 19 different values of
$\sigma \in [0,1.2]$ on $100$ different realizations at least $5000$
independent measurements are taken in equilibrium.\\
Since it is not known beforehand, where the critical temperatures \(T_c\)
are located, the Wolff cluster algorithm is used at every
temperature. Albeit the efficiency of the algorithmic procedure was
not examined for every temperature, the speed up near criticality
should be worth the moderate slow down at other temperatures.\\

@@

magnetization, the susceptiblity and the Binder cumulant

@@

        The same procedure is used on the Binder cumulant $g$ and the
        magnetization $|m|$ to determine the critical exponents

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[scale=1]{plots/Binder_over_Correlation_All}
    \caption[Binder cumulant over two-point finite-size correlation function divided by system size]
    {
        Binder cumulant $g$ over two-point finite-size correlation function
        divided by system size $L$. The datapoints for different system sizes
        are drawn with different symbols, while the datapoints for different
        graph ensembles are drawn with different colors. Anyway, all points
        fall on one curve within errorbars.
        %~ The inset zooms into the plot to show that
        %~ all datapoints fall within errorbars onto one curve.
    }
    \label{fig:binderOverCorr}
\end{figure}
If the Binder cumulant
\[g = \frac{3}{2}\brac{1-\frac{\avgR{\avg{m^4}}}{3\avgR{\avg{m^2}^2}}}\]
is plotted over $\xi$ for different $\sigma$, $L$ and $T$ as shown in
Fig.~\ref{fig:binderOverCorr}, all data points fall on the
same curve, which confirms that this IFM on proximity graphs is in the
same universality class as on the square lattice, i.e.~$\sigma=0$.

This study examines the critical temperatures $T_c$ for different values of $\sigma$.
Therefore the knowledge that the Binder cumulants $g$ for different
system sizes $L$ intersect at $T_c$ \cite{Binder1981} as shown in Fig.~\ref{sfig:Tc:binder}
%~ \begin{figure*}[hbtp]
    %~ \centering
    %~ \subfigure{
        %~ \label{sfig:Tc:binder}
        %~ \includegraphics[scale=1]{plots/binder}
    %~ }
    %~ \subfigure{
        %~ \label{sfig:Tc:RNG}
        %~ \includegraphics[scale=1]{plots/Tc_RNG}
    %~ }
    %~ \subfigure{
        %~ \label{sfig:Tc:GG}
        %~ \includegraphics[scale=1]{plots/Tc_GG}
    %~ }
    %~ \caption[Critical Temperature over Different Disorder Parameters]
    %~ {
        %~ Critical temperatures \(T_c\) are obtained by finding the intersections
        %~ of the Binder parameters $g$ for different system sizes $L$.
        %~ They are plotted over different disorder parameters \(\sigma\).
        %~ Interesting points are the jump and rise of the GG at small
        %~ \(\sigma\) and the plateau on the RNG for small \(\sigma\).
    %~ }
    %~ \label{fig:Tc}
%~ \end{figure*}
\begin{figure*}[hbtp]
    \subfigure[]{
        \label{sfig:Tc:binder}
        \includegraphics[scale=1]{plots/binder}
    }
    \subfigure[]{
        \label{sfig:Tc:RNG}
        \label{sfig:Tc:GG}
        \includegraphics[scale=1]{plots/Tc_both}
    }
    \subfigure[]{
        \label{fig:TcK}
        \includegraphics[scale=1]{plots/TcK}
    }
    \caption[Critical Temperature over Different Disorder Parameters]
    {
        \subref{sfig:Tc:binder} Critical temperatures \(T_c\) are obtained by finding the intersections
        of the Binder parameters $g$ for different system sizes $L$.
        \subref{sfig:Tc:RNG} They are plotted over different disorder parameters \(\sigma\).
        Interesting points are the jump and rise of the GG at small
        \(\sigma\) and the plateau on the RNG for small \(\sigma\).
        \subref{fig:TcK} \(T_c\) is plotted in a log-log plot as a function of the degree $K$.
        The lines are fits to a power law function \(T_c = aK^b\)
        ignoring the ``bulk" of points in the lower left and upper right, where
        deviations from the power law become obvious.
        For the RNG the fit yields $b = 1.349(2)$ with $\chi_\mathrm{red}^2 = 1.9$
        and for the GG  $b = 1.300(5)$ with $\chi_\mathrm{red}^2 = 0.8$
    }
    \label{fig:Tc}
\end{figure*}
is used.
Since \(g\) is only measured for discrete values of \(T\),
the points have to be interpolated to find the intersection. Therefore
a \emph{cubic spline} \cite{press2007numerical} interpolation %footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
is calculated for the measured points.
%~ Cubic spline interpolation is a piece-wise fitting of polynoms of
%~ degree three which are joined under the condition to be at least two
%~ times continuously differentiable.
%~ This interpolation type has the
%~ advantage that it is only influenced by local points so that the
%~ plateaus at low and high \(T\) do not influence the interpolation in
%~ the vicinity of \(T_c\) -- in contrast to, e.g.\ an polynom fit of
%~ degree 4, which has to be restricted to the vincinity of \(T_c\) to
%~ yield meaningful results.
An even better method would be the
\emph{multiple histogram} method \cite[p. 219ff]{NewmanBarkema1999}.
But the simple cubic spline interpolation seems to deliver results that
are good enough, because the temperatures of the measurements are
sufficiently near to each other. Also a cubic spline interpolation is
far easier to obtain.

The first oddity of the GG in Fig.~\ref{sfig:Tc:GG} which needs to be addressed is
the jump of $T_c$ close to $\sigma = 0$, where it jumps from $T_c(0) = 2.269(1)$
to $T_c(0.03) = 2.851(1)$ at the next measured temperature. This is easily explainable,
because the square lattice at $\sigma = 0$ is a very special case for the
GG and at smallest deviations from the square lattice new edges arise in
the GG, which lead to a stronger coupling of spins such that the system stays
ferromagnetic at higher temperatures.

@@

The critical temperature $T_c$ decreases with increasing $\sigma$, which
is expected, since the number of edges decreases, which can be seen in
Fig.~\ref{fig:RNG_sigma}. With loosely coupled spins, the temperature
needed to disturb the ferromagnetic phase is lower than with strongly coupled
spins. To quantify the influence of this, $T_c$ is plotted over the
degree $K$, i.e.~the mean number of neighbors each spin has, in Fig.~\ref{fig:TcK}.
For a given graph type, $T_c$ can be derived approximately by a power law
from $K$. But there are deviations from this behavior, which reflect
at least the influence of the coupling constant $J$.
